---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EGM

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/EGM)](https://CRAN.R-project.org/package=EGM)
[![R-CMD-check](https://github.com/shah-in-boots/EGM/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shah-in-boots/EGM/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/shah-in-boots/EGM/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/shah-in-boots/EGM/actions/workflows/test-coverage.yaml)
[![pkgdown](https://github.com/shah-in-boots/EGM/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/shah-in-boots/EGM/actions/workflows/pkgdown.yaml)
[![R-CMD-check](https://github.com/shah-in-boots/egm/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shah-in-boots/egm/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The purpose of `{EGM}` is to work with electrophysiology (EP) signal data to help understand and simplify the complexity of complex, multi-channel electrical signal data.
The target audience is those working, in particular, with *cardiac electrophysiology data*, from intracardiac electrograms to surface electrocardiography.
The package is heavily inspired by and gains additional functionality from the [Waveform Database (WFDB) software package](https://physionet.org/content/wfdb/10.7.0/).

The goals and major arms of this software are...

1. Adapt `WFDB`-compatible signal data to an `R` format that is interchangeable
1. Provide simple visualization tools to work with short elements of raw signal data
1. Allow for annotation of intracardiac electrograms in an interactive manner
1. Train and allow development of learning algorithms for the evaluation of multi-channel time series data

Please see the vignettes for further details on usage.

## Installation

You can install the released version of `{EGM}` from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
#install.packages("EGM")
```

And the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("shah-in-boots/EGM")
```
