---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EGM)
```

# Reading in Data

Thie software supports reading in certain types of raw cardiac electric signal currently. 
This includes both intracardiac and extracardiac data.
Please see `read_muse()` and `read_lspro()` as examples.
If additional formats are requested, please [file an issue](https://github.com/shah-in-boots/EGM/issues) and provide a sample file (which primarily requires signal, in whatever format, and meta-information about the individual channels).

Here is a simple example of taking a MUSE XML file and converting it to digital signal.
This was tested against the 9th version of the MUSE XML format.

```{r}
# Read in data
fp <- system.file('extdata', 'muse-sinus.xml', package = 'EGM')
xml <- readLines(fp)
head(xml)

# Instead, can read this in as a MUSE XML file
# Now as an `egm` class
ecg <- read_muse(fp)
ecg

# Can now plot this easily
ggm(ecg) + 
  theme_egm_light()
```

Similarly, intracardiac recordings obtained through LSPro can be read in as well. The function itself documents how this generally work.

```{r}
# Read in data
fp <- system.file('extdata', 'lspro-avnrt.txt', package = 'EGM')
lspro <- readLines(fp)
head(lspro, n = 20)

# Instead, read this as signal, breaking apart header and signal data
# Presented as an `egm` class object
egram <- read_lspro(fp)
egram

# Similarly, can be visualized with ease
ggm(egram, channels = c('HIS', 'CS', 'RV'), mode = NULL) +
	theme_egm_dark() 
```

# Class Introduction

The `{EGM}` package introduces a specific data-oriented class called `egm` (note the *lower-case* spelling compared to the package name). 
This class is the primary data structure, and allows for compatibility within multiple signal types, including when reading in WFDB-formatted data.
Once in this class, everything can be written out as well - with the preferred option being for the stated `WFDB` format.
